Tackling discrepancies in freshwater invertebrate trait databases: Harmonising across continents and aggregating taxonomic resolution

### 2021-02-10 Paper/Results/SI.tex
10.02.: Brook Edits Pt.6

\subsubsection*{Taxonomic hierarchy in the trait datasets used for comparisons with assigned traits at family-level}
\label{sec:taxonomic_hierarchy}
% \begin{figure}[H]
%     \centering
%     \includegraphics[width=16.5cm, height=10cm]{taxonomic_hierarchy_EU.png}
%     \caption{Number of genera per family and species per genus for the European trait dataset. For better visual display only families with more than 10 genera are displayed.}
%     \label{fig:tax_hierarchy_EU}
% \end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=16.5cm, height=10cm]{taxonomic_hierarchy_NOA.png}
    \caption{Number of genera per family and species per genus for those families of the North American trait dataset that have been compared to assigned traits at family level. For better visual display only families with more than 15 genera are displayed.}
    \label{fig:tax_hierarchy_NOA}
\end{figure}

>>>>

\subsubsection*{Taxonomic hierarchy in the trait datasets used for comparisons with assigned traits at family level}
\label{sec:taxonomic_hierarchy}
% \begin{figure}[H]
%     \centering
%     \includegraphics[width=16.5cm, height=10cm]{taxonomic_hierarchy_EU.png}
%     \caption{Number of genera per family and species per genus for the European trait dataset. For better visual display only families with more than 10 genera are displayed.}
%     \label{fig:tax_hierarchy_EU}
% \end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=16.5cm, height=10cm]{taxonomic_hierarchy_NOA.png}
    \caption{Number of genera per family and species per genus for those families of the North American trait dataset that have been compared with assigned traits at family level. For better visual display only families with more than 15 genera are displayed.}
    \label{fig:tax_hierarchy_NOA}
\end{figure}
